Supplementary material to: "Eddy covariance towers as sentinels of abnormal radioactive material releases"

### 2025-02-19 manuscript/manuscript.tex
acceptance formatting,typo fixes

\author{
	\href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Corresponding Author: Jemma Stachelek$^1$} \\
	$^1$ High Performance Computing Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
	\And
	Vachel A. Kraklow$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	Elizabeth Christi Thompson$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Lee Turin Dickman}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Emily Casleton}$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Sanna Sevanto}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Ann Junghans}$^4$ \\
	$^4$ Nuclear and Engineering Nonproliferation Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544
}

@@

\begin{figure}
	\centering
	\includegraphics[width=11cm]{__interaction_belon}
	\caption{Interaction plots at the BE-Lon site between air temperature ($C^{\circ}$) and $CO_2$ (ppm) for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm]{__rolling_fleurus}
	\caption{Time series plots (2004-2013) of rolling event detection analysis at the IRE site for the $CO_2$ and air temperature ($C^{\circ}$) variable pair. Event detection lines (orange), interaction effect size (blue), and event effect size (dashed black line) are shown in the top panels. The fraction of time that the wind direction was towards the particular tower (solid black) are shown in the corresponding bottom panels.}
	\label{fig:rolling}
\end{figure}

@@

The biggest improvements to our approach would likely come from coupling our data mining procedure with rigorous air pollutant dispersion modeling \cite[e.g.,][]{meszarosPredictabilityDispersionFukushimaderived2016}. This would eliminate the need for indirect estimation of material transport via uncertainty analyses and instead use simulation results to analytically determine the likely arrival and duration of material deposition. Further improvements could be made by incorporating knowledge about the composition of materials being deposited \citep{international2006iaea, meszarosPredictabilityDispersionFukushimaderived2016} and/or the interactions between material exposure and other environmental stressors \citep{mousseauPlantsLightIonizing2020}, which likely affects the severity and timing of ecosystem responses and by extension the fluxes being measured by a given tower. Such information may help disentangle potential interference of atmospheric contaminants with infrared measurement of $CO_2$ from declines in photosynthetic $CO_2$ uptake of contaminated vegetation given our observation that during and after the known abnormal release, the slopes of the relationships between $CO_2$ and air temperature become less negative than before the event, with lower than expected $CO_2$ at low air temperature. Although the chemical makeup of possible atmospheric contaminants is unknown, interference by iodine itself is unlikely to affect measurements of $CO_2$ given that the absorption spectra of iodine peaks at much shorter wavelengths around 10-7 m \citep{haynes2016crc} compared to that of $CO_2$ which peaks around 1700-2100 10-9 m (LICOR Biosciences Inc., Lincoln, NE).

>>>>

\author{
	% 1
	\href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Corresponding Author: Jemma Stachelek$^1$} \\
	$^1$ High Performance Computing Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
	\And
	% 4
	\textbf{Lee Turin Dickman}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\	
	\And
	% 2
	Vachel A. Kraklow$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\	
	\And
	% 5
	\textbf{Emily Casleton}$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\	
	\And
	% 3
	Elizabeth Christi Thompson$^3$ \\
	$^3$ Computer, Computational, and Statistical Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\	
	\And
	% 6
	\textbf{Sanna Sevanto}$^2$ \\
	$^2$ Earth and Environmental Sciences Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\And
	\textbf{Ann Junghans}$^4$ \\
	$^4$ Nuclear and Engineering Nonproliferation Division\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544
}

@@

\begin{figure}
	\centering
	\includegraphics[width=11cm]{__interaction_belon}
	\caption{Interaction plots at the BE-Lon site between air temperature ($^{\circ}C$) and $CO_2$ (ppm) for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm]{__rolling_fleurus}
	\caption{Time series plots (2004-2013) of rolling event detection analysis at the IRE site for the $CO_2$ and air temperature ($^{\circ}C$) variable pair. Event detection lines (orange), interaction effect size (blue), and event effect size (dashed black line) are shown in the top panels. The fraction of time that the wind direction was towards the particular tower (solid black) are shown in the corresponding bottom panels.}
	\label{fig:rolling}
\end{figure}

@@

The biggest improvements to our approach would likely come from coupling our data mining procedure with rigorous air pollutant dispersion modeling \cite[e.g.,][]{meszarosPredictabilityDispersionFukushimaderived2016}. This would eliminate the need for indirect estimation of material transport via uncertainty analyses and instead use simulation results to analytically determine the likely arrival and duration of material deposition. Further improvements could be made by incorporating knowledge about the composition of materials being deposited \citep{international2006iaea, meszarosPredictabilityDispersionFukushimaderived2016} and/or the interactions between material exposure and other environmental stressors \citep{mousseauPlantsLightIonizing2020}, which likely affects the severity and timing of ecosystem responses and by extension the fluxes being measured by a given tower. Such information may help disentangle potential interference of atmospheric contaminants with infrared measurement of $CO_2$ from declines in photosynthetic $CO_2$ uptake of contaminated vegetation given our observation that during and after the known abnormal release, the slopes of the relationships between $CO_2$ and air temperature become less negative than before the event, with lower than expected $CO_2$ at low air temperature. Although the chemical makeup of possible atmospheric contaminants is unknown, interference by iodine itself is unlikely to affect measurements of $CO_2$ given that the absorption spectra of iodine peaks at much shorter wavelengths around $10^{-7}$ m \citep{haynes2016crc} compared to that of $CO_2$ which peaks around 1700-2100 $10^{-9}$ m (LICOR Biosciences Inc., Lincoln, NE).

### 2025-02-19 manuscript/supplement.tex
acceptance formatting,typo fixes

\begin{document}
\title{Supplmentary material to: "Eddy covariance towers as sentinels of abnormal radioactive material releases"}
\date{}
\maketitle

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{__interaction_uswrc}
	\caption{Interaction plots at the BE-Bra site between air temperature ($C^{\circ}$) and $CO_2$ (ppm)for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction_bebra}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{__interaction_bevie}
	\caption{Interaction plots at the BE-Vie site between air temperature ($C^{\circ}$) and $CO_2$ (ppm) for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction_bevie}
\end{figure}

>>>>

\begin{document}
\title{Supplementary material to: "Eddy covariance towers as sentinels of abnormal radioactive material releases"}
\date{}
\maketitle

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{__interaction_uswrc}
	\caption{Interaction plots at the BE-Bra site between air temperature ($^{\circ}C$) and $CO_2$ (ppm) for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction_bebra}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=11cm]{__interaction_bevie}
	\caption{Interaction plots at the BE-Vie site between air temperature ($^{\circ}C$) and $CO_2$ (ppm) for the period of the known abnormal release (A) and an arbitrary non-release period (B). Also shown is the distribution of all interaction effect sizes (gray) compared with the effect size of the time period shown in the corresponding left panels (orange, C, D).}
	\label{fig:interaction_bevie}
\end{figure}
